### 2018-12-28 papers/journal/experiments.tex
Imroved introduction section and Experiments section

\textbf{{\sattool} (Bounded model checker based tool)}:
The {\sattool} tool is implemented using model checking tool for C program CBMC~\cite{clarke2004tool}.
%
CBMC is a Bounded Model Checker for C and C++ programs. 
%
Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC checks the verified property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.

The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
CBMC front end accepts ANSI-C programs with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
%

In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes. 
%		
The correspondence relationship between connectedness conditions
and guarantees for steady state were expressed as assertions to be checked. 
%		
Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, CBMC verifies the properties by executing the following steps:
	\begin{itemize}
	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
depth iff the Boolean formula is valid.
	\item Check (using a SAT solver) validity of the verification condition. CBMC reports successful verification if the formula is found to be valid. If not, then CBMC produces a counterexample,
an assignment to the variables of the model, that is a witness to the violation of the property.
	\end{itemize}

CBMC has a built-in SAT solver called MiniSat~\cite{sorensson2005minisat}, but it is also possible to use various other SAT solver blackboxes for property verification. Besides using MiniSat as a default SAT solver for our model, we have used different SAT solvers for the verification of the property, particularly CryptoMiniSat~\cite{soos2016cryptominisat} which was the winner of SAT 2015 Competition~\cite{balyo2016sat}. 
%		
MiniSat performed satisfactorily in comparison to other SAT solvers.

\textbf{{\smttool} (SMT based tool)}:
	We have implemented the encodings for each variants using the python interface of Z3 in a tool {\smttool}. 
%
Our tool allows the user to choose a model and the size
of the network besides other parameters like connectivity and number of parallel edges. 
%		
It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model (a satisfying assignment that respects the constraints). 
%
This tool also translates the satisfying model found by Z3 into
a VTS and presents a visual output to the user in form of annotated graph. 
%
We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.
%

\textbf{{\qbftool} (QBF based universal condition):}
{\qbftool} is developed in C++ and uses~\zthree~\cite{z3} infrastructure and implement the encodings of the VTS in QBF form (presented in section 6.5). 
%
Since some of the formulas involve alternation of quantifiers over
Boolean variables Z3 is not a suitable choice for those examples.
%
We translate the formulas created by Z3 tool into a standard
QDIMACS~\cite{qdimacs} format and use as an input for QBF solvers. 
%
We use~\depqbf~\cite{lonsing2010depqbf} for solving the QBF formulas.

@@

\input{synth-table}
We have implemented the synthesis  encodings in a tool
called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can not only synthesize the above-discussed queries, but also their
combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.

\subsection{Results}

To illustrate usability of our tool in the last column of the Table~\ref{tab:smt-grph}, we present the minimum connectedness needed for the different variants after applying our tool for sizes from 2 to 10. 
%
We found no graph for the variant A with constraints Ann and Aen. 
%
Replacing constraint on the node of Ann with Anb (variant B)
does not affect the outcome. 
%
If we allow every present molecule to stay active
(Ann) but constraint the edge by a boolean function (Aeb) the resultant VTS has to be at least 3-connected. 
%
Similarly, the results for other cases are presented in the table.

@@

In Table~\ref{tab:smt-grph}, we present the running times for the search of
VTSs of sizes 2 to 10 that satisfy the variants.
and compare with the {\sattool}.
%
For the comparison between both encodings we have fixed the total
number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and
$|M| = 2|N| + 1$ for $|N| = 2$.
%
For each variant, we fix maximum number of parallel
edges to 2.
%
In the table we have shown comparison for specific connectivity, for
example variant A is checked against any graph with connectivity 2,
variant B with connectivity 3 similarly for the rest of the Variants.
%

We have compared our performance with the performance of our earlier
CBMC based implementation (old-encoding).
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 s
ecs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
Using this encoding in comparison to the old one, not only we got effi
ciency improved for finding a SAT model but also did better in the cas
e of refutation that no model exist (Table 2 Variant A timing comparis
on and Variant D with N =2). 
%
Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ n
odes.

>>>>

\textbf{{\sattool} (Bounded model checker based tool)}:
	We have implemented the encodings for different variants of VTS (presented in section 6.2) using CBMC, a Bounded Model Checker, for C and C++ programs. 
%
%Unlike a general model checker~\cite{cimatti2002nusmv}, CBMC
%
The tool verify property for all the possible states, only up to a certain “depth,” a parametric limit on the size of the model.
%
The depth of model is specified by the user and can be  incrementally increased to a desired value.
%
The CBMC architecture consists of a C-language front-end (CFE) and a SAT Solver back-end (SAT). 
%
CBMC front end accepts ANSI-C programs with some special annotations (called assumes and assertions) to express constraints on the model and properties to be checked. 
%	
\todo{SA: CBMC Diagram}	
In our experiments, the vesicle transport network was modelled as a non-deterministic C-program manipulating a graph with labelled edges with the fusion rules and steady state properties expressed as constraints using assumes. 
%		
The correspondence relationship between connectedness conditions
and guarantees for steady state were expressed as assertions to be checked. 
%		
Given an exploration depth provided by the user, which in our case corresponds to the size of the graph, {\sattool} verifies the properties by executing the following steps:
	\begin{itemize}
	\item Convert (using CFE) the model and the properties into a Boolean formula (verification condition) such that the property is true of all behaviors of the model up to the specified
depth iff the Boolean formula is valid.
	\item Check (using a SAT solver) validity of the verification condition. {\sattool} reports successful verification if the formula is found to be valid. If not, then {\sattool} produces a counterexample,
an assignment to the variables of the model, that is a witness to the violation of the property.
	\end{itemize}
For our experimentation purpose, the SAT solver backend used were MiniSat~\cite{sorensson2005minisat}, and CryptoMiniSat~\cite{soos2016cryptominisat}, the winner of SAT 2015 Competition~\cite{balyo2016sat}.

%CBMC has a built-in SAT solver called MiniSat~\cite{sorensson2005minisat}, but it is also possible to use various other SAT solver blackboxes for property verification. Besides using MiniSat as a default SAT solver for our model, we have used different SAT solvers for the verification of the property, particularly CryptoMiniSat~\cite{soos2016cryptominisat} which was the winner of SAT 2015 Competition~\cite{balyo2016sat}. 
%		MiniSat performed satisfactorily in comparison to other SAT solvers.

\textbf{{\smttool} (SMT based tool)}:
	We have implemented the encodings for each variants (presented in section 6.1) using the python interface of Z3 in a tool {\smttool}. 
%
The tool allows the user to choose a model and the size
of the network besides other parameters like connectivity and number of parallel edges. 
%		
It uses Z3 Python interface to build the needed constraints and applies Z3 solver on the constraints to find a model (a satisfying assignment that respects the constraints). 
%
This tool also translates the satisfying model found by Z3 into
a VTS and represent a visual output to the user in form of coloured annotated graph. 
%
%We also visually report the dropped edges required to disconnect the graph, it gives information about the connectivity of the graph.
%

\textbf{{\qbftool} (QBF based universal condition):}
{\qbftool} is developed in C++ and uses~\zthree~\cite{z3} infrastructure and implement the encodings of the VTS in QBF form (presented in section 6.5). 
%
Since some of the formulas involve alternation of quantifiers over
Boolean variables Z3 is not a suitable choice for those examples.
%
We translate the formulas created by Z3 tool into a standard
QDIMACS~\cite{qdimacs} format and use it as an input for QBF solvers. 
%
We have used~\depqbf~\cite{lonsing2010depqbf} for solving the QBF formulas.

@@

\input{synth-table}
We have implemented the synthesis encodings (presented in section 6.6) in a tool
called~\ourtool\footnote{{\url{https://github.com/arey0pushpa/pyZ3}}}.
%
The tool takes a partially defined VTS as input in a custom designed
input language.
%
The input is then converted to the constraints over VTS using the {\qbftool} interface. 
%
The tool can not only synthesize the discussed queries, but also their
combinations.
%
For example, our tool can modify labels of nodes or edges while
learning activity functions.

\subsection{Results}
The results and timings of three blocks of the {\vtstool} are presented in the table~\ref{tab:smt-grph}, for both {\sattool} and {\smttool}, in table~\ref{tab:qbf-graph} for {\sattool} and in table~\ref{tab:synth-graph} for~{\ourtool}.

%To illustrate usability of our tool in the last column of the Table~\ref{tab:smt-grph}, we present the minimum connectedness needed for the different variants after applying our tool for sizes from 2 to 10. 
%%
%We found no graph for the variant A with constraints Ann and Aen. 
%%
%Replacing constraint on the node of Ann with Anb (variant B)
%does not affect the outcome. 
%%
%If we allow every present molecule to stay active
%(Ann) but constraint the edge by a boolean function (Aeb) the resultant VTS has to be at least 3-connected. 
%%
%Similarly, the results for other cases are presented in the table.

@@

In Table~\ref{tab:smt-grph}, we present the running times for the search of
VTSs for {\smttool} of sizes 2 to 10 that satisfy the variants and compare with the {\sattool}.
%
For the comparison between both encodings we have fixed the total
number of molecules to be $|M| = 2|N|$ for $ |N|> 2$ and $|M| = 2|N| + 1$ for $|N| = 2$.
%
For each variant, we fix maximum number of parallel
edges to 2.
%
In the table we have shown comparison for specific connectivity, for
example variant A is checked against any graph with connectivity 2,
variant B with connectivity 3 similarly for the rest of the Variants.
%

%We have compared our performance with the performance of our earlier CBMC based implementation (old-encoding).
%
For example, the formula for variation F, the total number of
compartments ($|N|$) equals to 10, returns in 129.78 minutes (7786.8 s
ecs)
with a SAT result.
%
In comparison, CBMC results in OUT OF MEMORY for $|N|$ greater than 5.
%
``!'' indicate that the constraints were unsatisfiable.
%
Using this encoding in comparison to the old one, not only we got effi
ciency improved for finding a SAT model but also did better in the cas
e of refutation that no model exist (Table 2 Variant A timing comparis
on and Variant D with N =2). 
%
Hence with the use of this novel encoding, we are able to scale the system to a much larger compartmentalized system, especially to
eukaryotic cells with a total number of 10 compartments.
%
Furthermore, we experimented with limits of our tools and found
that $\zthree$ was able to solve the constraints up to $\sim{14-18}$ n
odes.

### 2018-12-28 papers/journal/intro.tex
Imroved introduction section and Experiments section

First, we will give an overview of the VTS mechanism and then will sketch out a few interesting problems that are key to the understanding of the VTS.
%
%\textbf{Components of the vesicle transport network}:
The vesicle transport network is used by cells to transport molecules across compartments.
% 
The mechanism of vesicle transport can roughly be broken down into two steps: budding of vesicles from the source compartment and their fusion with the target compartment.
%
Vesicle budding involves three steps:
\begin{enumerate}
	\item  \textbf{Sorting of cargo molecules by cytosolic adaptor molecules}. 
	Cargo adaptors bind to short linear stretches of amino acids in the cargo molecules called sorting signals and thereby sequester them for packaging. 
	%
	Different adaptor proteins act at different compartments, for eg., sec23/24 is required
	for packaging vesicles that form at the ER, the AP2 adaptor is used for packaging vesicles at the plasma membrane, etc. 
	%
	Adaptors are recruited to the source compartments through interactions with
	the lipids that form the source compartment's membrane, and interactions with Arf/Sar GTPases which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.

	\item \textbf{Membrane deformation, which involves cytosolic coat proteins}.
	Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
	%
	These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
	%
	A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
	%
	Clathrin, COP2 and COP1 are the three major kinds of coat proteins
	in eukaryotic cells. 
	%
	The clathrin coat operates at multiple compartments, and can interact with
	multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}

	\item \textbf{Pinching of vesicles from the source compartment by dynamin}.
	The final step in vesicle formation is its piching off from the source compartment.
	%
	This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}
\end{enumerate}

Vesicle fusion involves two steps:
\begin{enumerate}
	\item \textbf{Recognition of the correct target compartment}. 
	This is a complex process involving Rab
	GTPases and tethering complexes:

	\begin{enumerate}[label=(\roman*)]
		\item \textbf{Rab GTPases}  are small proteins which occur in two forms: the membrane associated and active
		GTP bound form, and the cytosolic and inactive GDP bound forms. 
		%
		Different compartments of the
		cell are associated with a different type of Rab protein. In their active form, Rabs recruit many
		downstream proteins, including tethering complexes, fusion regulators, motor proteins, sorting
		adaptors, etc, to the membrane they are associated with. 
		%
		The proteins that are recruited by active
		Rabs are called Rab effectors.
		%
		Rab activity is controlled by two proteins: GEFs turn Rabs on and
		GAPs turn them off. 
		%
		Each Rab has its own specific GEF and GAP. In some cases, GEFs and GAPs
		themselves can be Rab effectors, thus generating feed-forward and feedback loops. 
		%
		In their cytosolic, inactive form, Rabs are complexed with GDI proteins, and it is in this form that Rabs are presented to membrane bound GEFs for activation~\cite{muller2018molecular}

		\item \textbf{Tethering complexes} sequester vesicles to their target compartments and regulate SNARE
		proteins, which enable vesicle fusion. 
		%
		Tethers are believed to bind to SNAREs and function as
		chaperones for SNARE complex assembly which is the ultimate step in membrane fusion. 
		%
		There are two types of tethering complexes: multi subunit tethers and long coiled-coil tethers:

		\begin{enumerate}[label=(\alph*)]
			\item \textbf{Coiled coil} tethers are long, single subunit proteins. 
			%
			These tethers are believed to bind the
			vesicle on one end and the target compartment on the other end, thereby bridging the two before
			fusion.
			%
			A clear mechanism for action of these tethers is missing, but based on their interactions with
			other proteins of the traffic machinery, some hypotheses as to their mechanism of action have been
			put forth. 
			%
			Golgins, coiled coil tethers that are anchored at the Golgi by a transmembrane domain, contain a large number of binding sites for Rab GTPases. 
			%
			Thus, golgins might capture vesicles by
			binding vesicle-associated Rab proteins. 
			%
			Golgins also contain domains which can sense membrane
			curvature, which they could be using to recognize vesicles. 
			%
			They might also be interacting directly
			with vesicle SNAREs~\cite{baker2016chaperoning}.

			\item \textbf{Multi-subunit tethering complexes (MTCs)} are composed of three or more different
			subunits.
			%
			MTCs are known to interact with vesicle coat proteins, Rab GTPases, SNAREs and SM proteins.
			%
			For example, the HOPS complex, which is required for homotypic (fusion of two identical
			membranes) and heterotypic fusion in the endo-lysosomal system, was shown to tether membranes
			through its interactions with the membrane-associated Rab GTPase Ypt7, acidic phospholipids and
			SNAREs. 
			%
			The HOPS complex binds both individual SNAREs and SNARE complexes. It also
			seems to protect assembling trans-SNARE complexes from premature disassembly. 
			%
			Another example is given by the Dsl1 complex, which is anchored to the ER membrane through interactions
			with t-SNAREs. 
			%
			At the other end, the Dsl1 complex contains multiple binding sites for COPI
			(vesicle coat that is present on vesicles produced by the Golgi). 
			%
			This structure suggests that the Dsl1
			complex functions as a tether connecting COPI-coated vesicles to their target organelle, the ER~\cite{baker2016chaperoning}.

		\end{enumerate}

	\end{enumerate}

	\item \textbf{Fusion of vesicle with the target compartment} is brought about by SNARE proteins. 
	%
	SNAREs
	are defined by a 60- to 70-residue SNARE motif. Most SNAREs are anchored to the membrane by
	their C-terminal transmembrane helices. 
	%
	The formation of a productive SNARE complex requires
	the formation of a four-helix bundle containing four different SNARE motifs. Usually, one of these
	motifs is contributed by the SNARE on the vesicle membrane (v-SNAREs), and the other three
	motifs by SNAREs on the membrane of the tartget compartment (t-SNAREs). 
	%
	Alternatively, they
	can be defined by their amino acid sequences as R-, Qa-, Qb-, and Qc-SNAREs. A few SNARE
	proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs.
	%
	Most v-SNAREs are RSNAREs, and most t-SNAREs are Q-SNAREs~\cite{yoon2018snare}.

\end{enumerate}

@@

\textbf{Major paths in the vesicle transport network}:
Molecules traverse the cell in a series of vesicles, and there are two major such routes of transport in all eukaryotic cells:
\begin{enumerate}
	\item The secretory route takes proteins from the ER, their site of production, to the plasma membrane, from where they are secreted out of the cell. Cargo proteins leave the ER in COP2 coated vesicles which fuse with the Golgi apparatus. The golgi apparatus is where proteins get modified, for example by the addition of carbohydrate side-chains. Subsequently, proteins destined for secretion are packaged into clathrin coated vesicles which fuse with the plasma membrane, thus releasing their contents to the outside of the cell\cite{alberts2002molecular}.
	\item the endocytic routetakes proteins from the outside of the cell through the plasma membrane to the endocytic compartments, where they are digested. Cargo from the outside of the cell is taken in in the form of clathrin coated vesicles which form at the plasma membrane. These vesicles fuse amongst themselves in a process called homotypic fusion to generate the early endosomal compartments. Early endosomes undergo changes in their composition due to ongoing vesicle traffic and maturee into late endosomes. This maturation is concomitant with a switch the Rab protein they are associated with; the Rab5 associated early endosomes mature into Rab7 associated late endosomes\cite{rink2005rab}. Late endosomes then fuse with lysosomes, where all its contents get digested\cite{pryor2009delivery}.
\end{enumerate}

\textbf{Existential and universal condition:}
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent from the TGN (Trans-Golgi network) to the early and the late endosomes to transport enzymes, and vesicles are sent back from the endocytic compartments to the TGN to recycle sorting receptors\cite{progida2016bidirectional}. Also recently, evidence for unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi. The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}. 
%

@@

\textbf{Difficulty of the problem:}
The analysis of vesicle traffic systems is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
For example, we might want to check some conjecture of interest for all 3-connected graphs and
all possible variations of SNARE regulation rules. 
%
The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.

\textbf{Synthesis of VTS:}
Although vesicle-mediated traffic was discovered decades ago~\cite{wells2005discovery}, the picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident organelles within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}.

Completing the vesicle traffic network is a difficult task for many reasons: (1) the core vesicle transport network, which consists of a secretory and an endocytic route, is conserved across all eukaryotes, but the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different \cite{stoops2014trafficking,zhou2015arp2}, (2) although the basic traffic machinery is the same for all vesicle fusion events, the details of regulation can be different \cite{davletov2007regulation,di2010calcium}, (3) behaviour of traffic molecules in vitro is different from their behaviour inside cells \cite{furukawa2014multiple}, (4) molecules can have redundant routes within the cell \cite{shimizu2014compensatory,nakatsukasa2014nutrient}, and (5) it can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.

>>>>

First, we will give an overview of the VTS mechanism and then will sketch out a few interesting problems that are key to the understanding of the VTS.

\todo{SA:One para of BIO BACKGROUND related to VTS. Why they are Important history etc.}
%
%\textbf{Components of the vesicle transport network}:
The vesicle transport network is used by cells to transport molecules across compartments.
% 
The mechanism of vesicle transport can roughly be broken down into two big steps:
% budding of vesicles from the source compartment and their fusion with the target compartment.
%
the process of formation of a vesicle by budding from the membrane called as vesicle budding and the fusion of these transport vesicle with its target compartment called as vesicle fusion.

\todo{SA:Need a Diagram}Vesicle budding process involves series of steps, sorting and packaging of the molecules, membrane deformation and budding out from the compartment.
%
First the sorting of cargo molecules takes place by cytosolic adaptor molecules. 
%
Cargo adaptors bind to short linear stretches of amino acids in the cargo molecules called sorting signals and thereby sequester them for packaging. 
%
Then the different adaptor proteins act at different compartments, for eg., sec23/24 is required for packaging vesicles that form at the ER, the AP2 adaptor is used for packaging vesicles at the plasma membrane, etc.
%
Thereafter, adaptors are recruited to the source compartments through interactions with the lipids that form the source compartment's membrane, and interactions with Arf/Sar GTPases which signal the initiation of vesicle formation~\cite{paczkowski2015cargo}.

The next step is membrane deformation, which involves cytosolic coat proteins.
Coat proteins are recruited to the forming vesicle through their interaction with adaptor proteins. 
%
These are naturally curved proteins, and their assembly on membranes leads to membrane deformation.
%
A single kind of coat protein can bind to multiple kinds of adaptors, thereby allowing the packaging of multiple types of cargo within the same vesicle. 
%
Clathrin, COP2 and COP1 are the three major kinds of coat proteins in eukaryotic cells. 
%
The clathrin coat operates at multiple compartments, and can interact with multiple adaptors proteins, whereas the COP2 and COP1 coat are only involved in vesicle formation at a single compartment; the ER and the Golgi respectively~\cite{faini2013vesicle}.

The final step is budding of the vesicles from the source compartment.
% by dynamin.
%	The final step in vesicle formation is its pinching off from the source compartment.
	%
This process requires ATP and is performed by the cytosolic dynamin proteins, which are recruited to the vesicle neck by the coat proteins~\cite{cocucci2014dynamin}.
%
The transport vesicle is now ready for the transportation.

Vesicle fusion involves two types of events, recognition of the correct target compartment and fusion of the transport vesicle with it's target compartment.

	 \textbf{Recognition of the correct target compartment} is a complex process involving Rab
	GTPases and tethering complexes.
	% 
	 Rab GTPases are small proteins which occur in two forms: the membrane associated and active
		GTP bound form, and the cytosolic and inactive GDP bound forms. 
		%
		Different compartments of the
		cell are associated with a different type of Rab protein. In their active form, Rabs recruit many
		downstream proteins, including tethering complexes, fusion regulators, motor proteins, sorting
		adaptors, etc, to the membrane they are associated with. 
		%
		The proteins that are recruited by active
		Rabs are called Rab effectors.
		%
		Rab activity is controlled by two proteins: GEFs turn Rabs on and
		GAPs turn them off. 
		%
		Each Rab has its own specific GEF and GAP. In some cases, GEFs and GAPs
		themselves can be Rab effectors, thus generating feed-forward and feedback loops. 
		%
		In their cytosolic, inactive form, Rabs are complexed with GDI proteins, and it is in this form that Rabs are presented to membrane bound GEFs for activation~\cite{muller2018molecular}

	 \textbf{Tethering complexes} sequester vesicles to their target compartments and regulate SNARE
		proteins, which enable vesicle fusion. 
		%
		Tethers are believed to bind to SNAREs and function as
		chaperones for SNARE complex assembly which is the ultimate step in membrane fusion. 
		%
		There are two types of tethering complexes: multi subunit tethers and long coiled-coil tethers:
%		
 Coiled coil tethers are long, single subunit proteins. 
			%
			These tethers are believed to bind the
			vesicle on one end and the target compartment on the other end, thereby bridging the two before
			fusion.
			%
			A clear mechanism for action of these tethers is missing, but based on their interactions with
			other proteins of the traffic machinery, some hypotheses as to their mechanism of action have been
			put forth. 
			%
			Golgins, coiled coil tethers that are anchored at the Golgi by a transmembrane domain, contain a large number of binding sites for Rab GTPases. 
			%
			Thus, golgins might capture vesicles by
			binding vesicle-associated Rab proteins. 
			%
			Golgins also contain domains which can sense membrane
			curvature, which they could be using to recognize vesicles. 
			%
			They might also be interacting directly
			with vesicle SNAREs~\cite{baker2016chaperoning}.
		%	
			Multi-subunit tethering complexes (MTCs) are composed of three or more different
			subunits.
			%
			MTCs are known to interact with vesicle coat proteins, Rab GTPases, SNAREs and SM proteins.
			%
			For example, the HOPS complex, which is required for homotypic (fusion of two identical
			membranes) and heterotypic fusion in the endo-lysosomal system, was shown to tether membranes
			through its interactions with the membrane-associated Rab GTPase Ypt7, acidic phospholipids and
			SNAREs. 
			%
			The HOPS complex binds both individual SNAREs and SNARE complexes. It also
			seems to protect assembling trans-SNARE complexes from premature disassembly. 
			%
			Another example is given by the Dsl1 complex, which is anchored to the ER membrane through interactions
			with t-SNAREs. 
			%
			At the other end, the Dsl1 complex contains multiple binding sites for COPI
			(vesicle coat that is present on vesicles produced by the Golgi). 
			%
			This structure suggests that the Dsl1
			complex functions as a tether connecting COPI-coated vesicles to their target organelle, the ER~\cite{baker2016chaperoning}.

	 \textbf{Fusion of vesicle with the target compartment} is brought about by SNARE proteins. 
	%
	SNAREs
	are defined by a 60- to 70-residue SNARE motif. Most SNAREs are anchored to the membrane by
	their C-terminal transmembrane helices. 
	%
	The formation of a productive SNARE complex requires
	the formation of a four-helix bundle containing four different SNARE motifs. Usually, one of these
	motifs is contributed by the SNARE on the vesicle membrane (v-SNAREs), and the other three
	motifs by SNAREs on the membrane of the tartget compartment (t-SNAREs). 
	%
	Alternatively, they
	can be defined by their amino acid sequences as R-, Qa-, Qb-, and Qc-SNAREs. A few SNARE
	proteins, such as SNAP25, contain both Qb- and Qc-SNARE motifs.
	%
	Most v-SNAREs are RSNAREs, and most t-SNAREs are Q-SNAREs~\cite{yoon2018snare}.

@@

\textbf{Major paths in the vesicle transport network}:
Molecules traverse the cell in a series of vesicles, and there are two major such routes of transport in all eukaryotic cells.
%
	The secretory route takes proteins from the ER, their site of production, to the plasma membrane, from where they are secreted out of the cell.
	%
	 Cargo proteins leave the ER in COP2 coated vesicles which fuse with the Golgi apparatus.
	 %
	  The golgi apparatus is where proteins get modified, for example by the addition of carbohydrate side-chains. 
	  %
	  Subsequently, proteins destined for secretion are packaged into clathrin coated vesicles which fuse with the plasma membrane, thus releasing their contents to the outside of the cell\cite{alberts2002molecular}.
	  %
 The endocytic routetakes proteins from the outside of the cell through the plasma membrane to the endocytic compartments, where they are digested. 
 %
 Cargo from the outside of the cell is taken in in the form of clathrin coated vesicles which form at the plasma membrane. 
 %
 These vesicles fuse amongst themselves in a process called homotypic fusion to generate the early endosomal compartments. 
 %
 Early endosomes undergo changes in their composition due to ongoing vesicle traffic and maturee into late endosomes. 
 %
 This maturation is concomitant with a switch the Rab protein they are associated with; the Rab5 associated early endosomes mature into Rab7 associated late endosomes\cite{rink2005rab}. Late endosomes then fuse with lysosomes, where all its contents get digested\cite{pryor2009delivery}.
%
Other paths are used for cross talk between the secretory and the endocytic routes. For example, vesicles are sent from the TGN (Trans-Golgi network) to the early and the late endosomes to transport enzymes, and vesicles are sent back from the endocytic compartments to the TGN to recycle sorting receptors\cite{progida2016bidirectional}. Also recently, evidence for unconventional vesicle-mediated secretory routes have been found, which bypass the Golgi. The molecules involved in these routes are as yet unknown\cite{nickel2018unconventional}. 
%

@@

\todo{SA: Describe the model in graph terms and connect it to the topology question. ONE PAGE !}
\textbf{Difficulty of the problem:}
The analysis of vesicle traffic systems is a difficult problem
because of the combinatorial scaling of possible traffic topologies and regulatory rules. 
%
For example, we might want to check some conjecture of interest for all 3-connected graphs and
all possible variations of SNARE regulation rules. 
%
The number of graphs of specified connectivity grows exponentially with the number of nodes: Table~\ref{tab:threec} shows how many 3-edge-connected graphs~\cite{a052448-oeis} exist (without parallel or self edges) as node number N increases.

\textbf{Synthesis of VTS:}
Although vesicle-mediated traffic was discovered decades ago~\cite{wells2005discovery}, the picture of the vesicle transport network is far from complete; we do not yet know how many of the cellular proteins reach their resident organelles within the cell, and new vesicle routes are being discovered every year ~\cite{nickel2018unconventional,weill2018toolbox}. 
%
Completing the vesicle traffic network is a difficult task for many reasons: (1) the core vesicle transport network, which consists of a secretory and an endocytic route, is conserved across all eukaryotes, but the traffic network in different organisms \cite{richardson2015evolutionary,nishimoto2009differential,barlow2017seeing}, and even in different cell types within an organism can be different \cite{stoops2014trafficking,zhou2015arp2}, (2) although the basic traffic machinery is the same for all vesicle fusion events, the details of regulation can be different \cite{davletov2007regulation,di2010calcium}, (3) behaviour of traffic molecules in vitro is different from their behaviour inside cells \cite{furukawa2014multiple}, (4) molecules can have redundant routes within the cell \cite{shimizu2014compensatory,nakatsukasa2014nutrient}, and (5) it can be difficult to distinguish between the direct and indirect effects of experiments involving knock-downs or knock outs of traffic molecules \cite{hirst2004epsinr,mishev2013small}.
